---
title: "`reprex` Introduction"
subtitle: "DEOHS Coders Group"
author: "Chris Zuidema"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load.libraries.pacman, echo=FALSE, include=FALSE, eval=TRUE}
#-----load libraries pacman-----

# Load pacman into memory, installing as needed
my_repo <- 'http://cran.r-project.org'
if (!require("pacman")) {install.packages("pacman", repos = my_repo)}

# Load the other packages, installing as needed.
pacman::p_load(knitr, dplyr, reprex, VCA, palmerpenguins)

```


# Getting Help

The `reprex` package is designed to help you get help. We've covered getting
help in coders group in the past. You can review what we talked about
[here](https://github.com/deohs/r_onramp/blob/master/r_resources_and_getting_help.md#how-to-ask-for-help).
Basically, we suggested:

  * Do your homework carefully
  * Be clear, specific, and thorough
  * Be respectful and mature
  * Provide a reproducible example of your problem
  * Don't expect strangers on the Internet to solve your homework problems for you

Today we're going to focus on "Provide a reproducible example of your problem"
with the tidyverse `reprex` package.


# What is `reprex`?

`reprex` is a package that that makes it convenient to make a *repr*oducible
*ex*ample with the goal of making code you seek help with:

  * Code that actually runs
  * Code that the reader does not necessarily have to run
  * Code that the reader can easily run


# Introductory `reprex` Example

Lets say we need help with the following code chunk:

```{r struggle.bus}

# make some awesome factors
x <- factor("Can")
y <- factor("I")
z <- factor("code")

# view them
x
y
z

# combine x & y
c(x, y, z)

```

This is not what I expected! I was hoping for something more like: 

``` 
> c(x, y, z)

[1] Can I code
Levels: Can I code

```

So I need help and I need to send my code somewhere or to someone. The `reprex`
package helps do this.


# Steps to share your code with `reprex`

`reprex` makes it easy to share with others: 

  1. Highlight the code you want to `reprex` 
  2. Copy the code through shortcuts (Ctrl + C or Cmd + C) or Menu (Edit -> Copy)
  3. In the Console enter `reprex::reprex()` or just `reprex()` if the package
     is already loaded 
  4. `reprex` renders to the Viewer pane and is automatically available on your 
     clipboard. 
      * from here you can copy/paste into a document, email, GitHub, etc.


Let's practice with another chunk of code that, unlike our first example, fails
and does not run (as opposed to our first example that ran but gave unexpected
output).

```{r code.fail}

# # Load pacman, installing as needed
# if (!require("pacman")) {install.packages("pacman")}
# 
# # Load the other packages, installing as needed.
# pacman::p_load(dplyr, VCA)

df <- dplyr::storms

# visualize data
varPlot(form = wind  ~ year, Data = df, 
        VarLab = list(srt = 90) 
        )

```


## Sharing in an email

This is easy! Once the `reprex` is rendered in the viewer, it can just be
copied/pasted.


## Sharing in a GitHub Issue

We'll use our DEOHS [coders group repository](https://github.com/deohs/coders)
to demonstrate.

Find the "Issues" link, then the "New issue" link. You can paste the `reprex`
output right in the text box.

From there others can view the code and output or copy/paste it into their own R
session.


# `reprex` a File

You can also `reprex` a whole file:

```{r reprex.file}

reprex(input = "reprex_example_file.R")

```


# Capture a `reprex` when helping others

```{r reprex.clean}

# copy a reprex from the wild, then run
reprex_clean()

```


# Get clean code from your console

```{r reprex.rescue}

# copy code from your console, then run
reprex_rescue()

```


# Un-render a `reprex`

```{r reprex.invert}

# first create a `reprex` from a file
temp <- reprex(input = "reprex_example_file.R", outfile = file.path(tempdir()))

# then invert
reprex_invert(temp)

```

